
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.

```{r}
# Loads the library
library(gganimate)
# Other libraries that will be used
library(ggplot2)
library(tidyverse)
library(knitr)
df = read_csv('adult_census_missing (1).csv')
```

```{r}
df %>% ggplot(aes(x = education.num,
           y = age, color=workclass))+
  geom_point()+
  transition_states(sex)
```


2. Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.

```{r}
df %>% ggplot(aes(x = education.num,
                  fill=sex))+
  geom_bar(position = 'fill')+
  transition_states(education)
```

3. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.

```{r}
df2 = read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
```

```{r}
df2 %>% ggplot(aes(x = Cumulative_deaths,
                  fill=Country))+
  geom_bar(position = 'fill')+
  transition_states(Date_reported)
```

4. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 

```{r}
d1 = read_csv('https://covidtracking.com/data/download/all-states-history.csv')
```

```{r}
p1 <- d1 %>% 
  ggplot(aes(y=state, x=mean)) + 
  geom_col()+
  transition_states(month)+
  labs(x = 'Total Positive', 
       title = 'Month: {closest_state}')
animate(p1, nframes=400)
```

