
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|

```{r}
df = data.frame(Rank = c(0,1,2,3),
                Age = c(28,34,29,42),
                Name = c('Tom', 'Jack', 'Steve', 'Ricky'))
df
```


2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).

```{r}
df = read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
```


2. Show the names of the variables in the data

```{r}
names(df)
```


3. How many columns and rows the data have? 

```{r}
str(df)
```


4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?

```{r}
sum(is.na(df))
colSums(is.na(df))
```

Data shows there are no missing values.

5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 

```{r}
class(df$date)
str(df)
df$date = as.Date(df$date)
```

6. Capitalize the names of all the variables

```{r}
library(stringr)
str_to_title(names(df))
```


7. Find the average number of cases per day. Find the maximum cases a day.  

```{r}
mean(df$cases)
```

8. How many states are there in the data?  

```{r}
length(table(df$state))
```

9. Create a new variable `weekdays` to store the weekday for each rows. 

```{r}
df$weekdays = weekdays(df$date)
```

10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`. 

```{r}
library(dplyr)
df$death2 <- case_when(df$deaths>0 ~ 'has_death', df$deaths<1 ~ 'no_death')
table(df$death2)
table(df$death2)/length(df$death2)
```

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)

```{r}
summary(df$deaths)
```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r}
df$death3 = case_when(df$deaths<842 ~ 'low_death', df$deaths>=842 & df$deaths<= 12703 ~ 'mid_death', df$deaths>12703 ~ 'high_death')
table(df$death3)
```

13. Find the average cases in Rhode Island in 2021

```{r}
ri = df[(df$state=='Rhode Island'), ]
df2 = ri[(ri$date >= '2021-01-01')& (ri$date <= '2021-12-31'), ]
mean(df2$cases)
```

14. Find the median cases by weekdays in Rhode Island in 2021 

```{r}
by(df2$cases, df2$weekdays, median)
```

15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 

```{r}
df3 = df2[(df2$date>='2021-06-01')&(df2$date<='2021-09-30'),]
df3$month = months(df3$date)
by(df3$month, df3$cases, median)
```

16.  Find your own dataset, import it and implement the following functions on the data

```{r}
data = read.csv('https://bryantstats.github.io/math421/data/titanic.csv')
```
```{r}
head(data)
str(data)
names(data)
mean(data$Age)
min(data$Fare)
max(data$Age)
table(data$Pclass)
sum(is.na(data))
colSums(is.na(data))
class(data$Pclass)
cor(data$Pclass, data$Survived)
by(data$Fare, data$Survived, median)
data$Fare2 = ifelse(data$Fare>median(data$Fare),'High Fare', 'Average Fare')
data$classes = case_when(data$Pclass=='1' ~ 'Low Class', data$Survived==2 ~'Middle Class', data$Pclass=='3' ~ 'High Class')
```

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when

17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

```{r}
data$Survived = case_when(data$Survived<1 ~ 'Dead', data$Survived>0 ~'Alive')
```

```{r}
data$classes_2 = case_when(data$Pclass<'3' ~ 'Average Class', data$Pclass=='3' ~ 'Above Average Class')
```

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
